Data Preparation

### 2019-02-15 Data Preparation.Rmd
save cached results in folder `Cache`

---
title: "Data Preparation"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
---

@@

# Variable Engineering
## Program Data
The analysis performed on the course data is aimed at discoving what the contribution of each course is towards the fullfilment of the AoDs, and comparing different types of curricula, or programs, based on this infromation.

@@

  if(length(AoD) >= 1) d_AoD_assessment <- rbind(d_AoD_assessment,
                                                 as.tibble(cbind(observation,
                                                                 AoD)))
}
rm(map_assessment_AoD, observation, AoD, AoD_covered, assessments, i)
```

@@

Our dataframe contains many variables and rows that are either empty or meaningless for our analysis. First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor"). Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
```{r}
d_transcript <- d_transcript %>%
  # only keep one observation (with the final grade) per student-course
  filter(`Appraisal (Description)` == "Grade supervisor", `Appraisal Type`=="7055") %>%
  select(`Student Number`,
         `Module (Abbrev.)`,
         `Module (Desc.)`,
         `Program (Abbreviation)`,
         `Grade symbol`,
         `Academic Year`,
         `Academic Session`,
         `Number rep. attemp`) %>%
  rename(`Student ID` = `Student Number`,
         `Course ID` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         Grade = `Grade symbol`,
         `Study Program` = `Program (Abbreviation)`,
         Year_numerical = `Academic Year`,
         Period = `Academic Session`,
         `Number Repeated Attempt` = `Number rep. attemp`) %>%
  distinct
```

>>>>

---
title: "Data Preparation"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include = T}
knitr::opts_chunk$set(cache.path = "Cache/Data Preparation/")
```

@@

# Variable Engineering
## Course Data
The analysis performed on the course data is aimed at discoving what the contribution of each course is towards the fullfilment of the AoDs, and comparing different types of curricula, or programs, based on this infromation.

@@

  if(length(AoD) >= 1) d_AoD_assessment <- rbind(d_AoD_assessment,
                                                 as_tibble(cbind(observation,
                                                                 AoD)))
}
rm(map_assessment_AoD, observation, AoD, AoD_covered, assessments, i)
```

@@

Our dataframe contains many variables and rows that are either empty or meaningless for our analysis. First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor"). Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
```{r}

d_transcript <- d_transcript %>%

  # Remove variables with only one value
  select_if(
    function(x) n_distinct(x) > 1
  ) %>%

  # Remove variables with more than 99% NA
  select_if(
    function(x) mean(is.na(x)) < 0.99
  )

d_transcript <- d_transcript %>%

  # only keep one observation (with the final grade) per student-course
  filter(
    `Appraisal (Description)` == "Grade supervisor",
    `Appraisal Type`=="7055"
    ) %>%
  select(`Student Number`,
         `Module (Abbrev.)`,
         `Module (Desc.)`,
         `Program (Abbreviation)`,
         `Grade symbol`,
         `Academic Year`,
         `Academic Session`,
         `Number rep. attemp`) %>%
  rename(`Student ID` = `Student Number`,
         `Course ID` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         Grade = `Grade symbol`,
         `Study Program` = `Program (Abbreviation)`,
         Year_numerical = `Academic Year`,
         Period = `Academic Session`,
         `Number Repeated Attempt` = `Number rep. attemp`) %>%
  distinct
```
